---
title: 'DATA 607 - Assignment #3'
author: "Kory Martin"
date: "2/11/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Question #1

Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r import-data}
college_majors = read_csv('https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv', 
                          show_col_types = FALSE)

```


```{r filter-statistics-data majors}

college_majors %>% filter(str_detect(Major,"STATISTICS") | str_detect(Major,"DATA"))

```
## Question #2

Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r pressure, echo=FALSE}

string_1 = '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"'
string_2 = '[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry" '
string_3 = '[9] "elderberry"   "lime"         "lychee"       "mulberry" '
string_4 = '[13] "olive"        "salal berry"'

data_string = paste(string_1, string_2, sep="\n")
data_string = paste(data_string, string_3, sep="\n")
data_string = paste(data_string, string_4, sep="\n")

data_string

str_elements = str_extract_all(data_string, "[a-z]+\\s*[a-z]+")

num_elements = length(str_elements[[1]])
element_num = 1
new_string = ""
for (word in str_elements[[1]]) {
  #print(word)
  word_string = str_c("\"",word,"\"")
  if(element_num < num_elements ) {
    new_string = paste0(new_string, word_string,", ")  
  }
  else {
    new_string = paste0(new_string, word_string)  
  }
  #print(new_string)
  element_num = element_num+1
  #print(element_num)
}


new_string = paste0("(",new_string,")")
new_string = paste0("c",new_string)

print(new_string)
```

## Question #3

Describe, in words, what these expressions will match:
  
  - (.)\1\1
  
  This matches 3 consecutive matches of a character
  e.g. in string "422-3777", it would match 777
  
  - (.)(.)\\2\\1
  
  This matches a character followed by a second character repeated twice followed by the first character again. 
  e.g. in string "gamma", it would match amma
  
  - (..)\1
  
  This matches 2 characters repeated twice
  e.g. in string "cucumber", it would match cucu
  
  - "(.).\\1.\\1"
  
  This matches a character followed by any other character, followed by the first character, followed by any other character, followed by the first character
  e.g. in string "707372456", it would match 70737
  
  - "(.)(.)(.).*\\3\\2\\1"
  
  This matches any 3 characters, followed by 0 or more additional characters, followed by the 3rd character, then the 2nd character, and lastly the 1st character.
  e.g. in string "4563abc45643cba1231, it would match abc45643cba


## Question #4

Construct regular expressions to match words that:
  
  - Start and end with the same character: 
  
  ^(.).*\1$
  
  - Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.): 
  
  (..).*\1
  
  - Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.): 
  
  (.).*\1.*\1
